% \renewcommand{\bibname}{\fontsize{17pt}{18pt}\selectfont Appendix B: \\~\\\fontsize{23pt}{23pt} Bibliography} 
% \chapter{Bibliography}
\begin{thebibliography}{}
 % \thispagestyle{empty}
 \addcontentsline{toc}{chapter}{Bibliography}
% \addcontentsline{toc}{chapter}{\protect\numberline{B}{Bibliography}}
\bibitem{latexcompanion} 
Wellner, P. (1993). Interacting with paper on the DigitalDesk. Communications of the ACM, 36(7), pp.87-96. 

\bibitem{Mixed reality} 
Tech Times. (2017). Mixed Reality vs Virtual Reality vs Augmented Reality: What's The Difference?. [online] Available at: 
\\\texttt{http://www.techtimes.com/articles/189188/20161218/mixed-real\\ity-vs-virtual-reality-vs-augmented-reality-whats-the-differ\\ence.htm} [Accessed 4 Feb. 2017].

\bibitem{LeapMotion Hack}
Bedikian, R. and Bedikian, R. (2017). The Leap Motion Hackathon’s Augmented Reality Workspace. [online] Leap Motion Blog. Available at: 
\\\texttt{http://blog.leapmotion.com/hood-leap-motion-hackathons-augm\\ented-reality-workspace/} [Accessed 4 Feb. 2017].
 
\bibitem{AugmentDesktop}
Augment. (2017). Augment Desktop - Augment. [online] Available at:
\\\texttt{http://www.augment.com/technology/augment-desktop/} [Accessed 6 Feb. 2017].

\bibitem{HoloLens}
Microsoft HoloLens. (2017). Microsoft HoloLens. [online] Available at: 
\\\texttt{https://www.microsoft.com/microsoft-hololens/en-us} [Accessed 6 Feb. 2017].

\bibitem{Meta}
Metavision.com. (2017). Augmented Reality - Home | Meta Company. [online] Available at: 
\\\texttt{https://www.metavision.com/} [Accessed 6 Feb. 2017].

\bibitem{ARToolKit}
Artoolkit.org. (2017). Open Source Augmented Reality SDK | ARToolKit.org. [online] Available at:
\\\texttt{https://artoolkit.org/} [Accessed 7 Feb. 2017].

\bibitem{Vuforia}
Vuforia.com. (2017). Vuforia | Augmented Reality. [online] Available at: 
\\\texttt{https://www.vuforia.com/} [Accessed 7 Feb. 2017].

\bibitem{mono}
Mono-project.com. (2017). Home | Mono. [online] Available at:
\\\texttt{http://www.mono-project.com} [Accessed 7 Feb. 2017].


\bibitem{Survey} 
Anon, (2016). 1st ed. [ebook] Available at:
\\\texttt{https://www.perkinscoie.com/images/content/1/5/v2/158662/2\\016-VR-AR-Survey.pdf}
[Accessed 23 Nov. 2016]

\bibitem{Surveymonkey} 
Surveymonkey.com. (2016). SurveyMonkey - Log in. [online] Available at:
\\\texttt{https://www.surveymonkey.com/analyze/Z\_2BgXzn8HyDxH60BmP5b\\fosg8fMm\_2F2K00Yk8li\_2B1iaVk\_3D\#}
[Accessed 18 Oct. 2016].

\bibitem{LeapMotion} 
Developer.leapmotion.com. (2016). Unity | Leap Motion Developers. [online] Available at:
\\\texttt{https://developer.leapmotion.com/unity\#quick-setup}
[Accessed 18 Oct. 2016].

\bibitem{Unity}
Assetstore.unity3d.com. (2016). Asset Store. [online] Available at:
\\\texttt{https://www.assetstore.unity3d.com/cn/\#!/content/17591}
[Accessed 17 Nov. 2016].

\bibitem{MongoDB}
MongoDB. (2016). MongoDB and MySQL Compared. [online] Available at:
\\\texttt{https://www.mongodb.com/compare/mongodb-mysql?jmp=search\&utm\\\_source=google\&utm\_campaign=EMEA\_UK-IE\_Corp/Ent\_Brand\_Beta\_F\\M\&utm\_keyword=\%2Bmongodb\%20\%2Bmysql\&utm\_device=c\&utm\_network\\=g\&utm\_medium=cpc\&utm\_creative=154321209803\&utm\_matchtype=b\&\\\_bt=154321209803\&\_bk=\%2Bmongodb\%20\%2Bmysql\&\_bm=b\&\_bn=g\&gclid\\=CjwKEAiAsMXBBRD71KWOh6fcjRwSJAC5CNE1tMS\_-fBZ7EB\_CfKkXDsXZjY\\f1tqyYj61Jfj6KaYodRoCSw\_w\_wcB}  
[Accessed 20 Nov. 2016].


\bibitem{server}
Synchronous Server Socket Example. (2017). [online] Msdn.microsoft.com. Available at: 
\\\texttt{https://msdn.microsoft.com/en-us/library/6y0e13d3(v=vs.110).\\aspx} [Accessed 22 Feb. 2017].

\bibitem{Client}
Synchronous Client Socket Example. (2017). [online] Msdn.microsoft.com. Available at: 
\\\texttt{https://msdn.microsoft.com/en-us/library/kb5kfec7(v=vs.110).\\aspx} [Accessed 22 Feb. 2017].

\bibitem{Angular}
Docs.angularjs.org. (2017). AngularJS. [online] Available at: 
\\\texttt{https://docs.angularjs.org/guide/scope} [Accessed 28 Feb. 2017].


\bibitem{Tangible mixed reality desktop}
National University of Singapore. (2007). Tangible mixed reality desktop for digital media management. [online] Available at: 
\\\texttt{http://proceedings.spiedigitallibrary.org/proceeding.aspx?ar\\ticleid=1298425} [Accessed 8 Mar. 2017].

\bibitem{Mixed reality with education}
Hughes, C., Stapleton, C., Hughes, D. and Smith, E. (2005). Mixed Reality in Education, Entertainment, and Training. IEEE Computer Graphics and Applications, 25(6), pp.24-30.

\bibitem{Education2}
Anon, (2017). [online] Available at: 
\\\texttt{http://s3.amazonaws.com/academia.edu.documents/4810740/ar\_e\\du.pdf?AWSAccessKeyId=AKIAIWOWYYGZ2Y53UL3A\&Expires=14919240\\31\&Signature=FmiVcGYVmEa4jlC13Qfl51Z97J4\%3D\&response-content\-disposition=inline\%3\%20filename\%3DAugmented\_reality\_in\_educa\\tion.pdf} [Accessed 11 Apr. 2017].

\bibitem{Education3}
Scholar.lib.vt.edu. (2017). JITE v41n4 - Desktop Virtual Reality: A Powerful New Technology for Teaching and Research in Industrial Teacher Education. [online] Available at: 
\\\texttt{http://scholar.lib.vt.edu/ejournals/JITE/v41n4/ausburn} [Accessed 11 Apr. 2017].

\end{thebibliography}
