% Chapter 1

\chapter{Introduction} % Main chapter title

\label{Chapter1} % For referencing the chapter elsewhere, use 
Desktop metaphor developed by Xerox PARC led visionaries to predict the “paper- less office”, but the problem is that people like paper too much. After that, Pierre David Wellner from University of Cambridge tried to provide a Computer Augmented Environment for paper by using video camera and electronic projector [1]. In his project, three main functionalities were achieved, Calculator, PaperPaint, and DoubleDigitalDesk. Calculator enables user to select some numbers which could be recognized by the camera, and the answer will be projected to the paper after the computer finished the calculation. PaperPaint allows user to move a copy of anything he writes on the paper. DoubleDigitalDesk is a remote digital desktop which enables user to cooperate or play games. At the end of his research, Pierre discussed some potential directions for continuing work on this Digital Desktop and Augmented Environment, like getting rid of the tablet which used to allow pointing at projected images, and implementing electronic annotation of paper documents. With the booming of Mixed Reality technology, advanced devices and software development kit, the current technology provides more opportunities for developing new digital desktop. And the advanced VR headset improves the user experience and provides more options for developer to introduce more common computer functions (like task manager and weather forecast) into the virtual world.
\\
\\
Hybrid desktop is a project aimed at improving the university students studying and working efficiency and providing them a brand-new way to study. Hybrid means a combination of physical and electronic desktop. Compared with electronic desktop, it is hard for physical desktop to get access to large amount of materials, and especially when the final is approaching, students need to carry heavy paper with them which will be a burden, and physical documents are easy to lose and the capacity is limited as well. As time goes by, students will have more and more notebooks, and it is also difficult for them to manage these materials. If they only work with electronic documents, it is not convenient for them to take notes on the graphs, and highlight some important points. When people are drawing something, keyboard and mouse are especially hard to control. However, physical desktop can fix this problem. It is easier to interact, because using a pen to write down notes and draw diagrams can provide a much simpler way for students to express their idea accurately.
\\
\\
In conclusion, hybrid desktop will take advantages of both physical and electronic desktop. Users are not only able to get access to their module’s PDF or PPT slides and view them in an electronic way, but also interact with their physical documents (books and notes). This project is going to provide a comprehensive environment for students to study.  
