% Chapter Template

\chapter{Motivation} % Main chapter title

\label{Chapter2} % Change X to a consecutive number; for referencing 
Based on 2016 augmented and virtual reality survey report [10], within 10 years, AR and VR would produce revenue in the tens of billions of dollars. However, the majority of participants respond that the lack of compelling content and user experience was the most significant obstacle for AR/VR industry. And two-thirds of participants expect the AR market to surpass VR in revenue. Game, movies and television, live events and education are the top four sectors which respondents expect to see. But the biggest obstacle to mass adoption of VR technology is user experience and cost. These results indicate AR/VR market is full of potential, and these products should be more linked with people’s daily life.
\\
\\
The ultimate goal of Pierre David Wellner’s research on interacting with paper on digital Desktop is instead of making us work in the computer’s world, let us make it work in our world. In conclusion, the motivation of this project is to enhance the students after-school learning experience by allowing them to interact with physical and electronic materials by using Mixed reality technology. Although there has already existed some application which fits the idea of working with Mixed reality, the price and weight of the device are such a burden for users. So, developing a hybrid desktop based on smart phone which is a device that almost everyone has is very worthwhile. It ensures that most students are able to get access to it and they do not need to buy any other devices, using their portable smart phone is enough.

